# Database Structure

The package `DBI` was used to create the database and tables. I chose this directory structure so that it is nested in my root directory for easy import into R and for version tracking with Git. For organizational purposes, I placed it in my MASTERS folder, under the folder MetaAnalysis so that all files associated with my degree and proposed meta-analysis are in one, easy to locate folder. I chose to add folders for Code, Data, Figures, Manuscripts, README, and Results at your recommendation so that I can track and version control all incoming data, code that is created, and eventual Figures, Results, and Manuscripts that are developed from the eventual analysis. The README folder will track all inputs to these folders as my metadata. The MetaAnalysis folder can then be zipped and shared at the conclusion of the study for anyone that may want to replicate my methods.

## Database Creation

```{r, eval = FALSE, echo = TRUE}
metabeaver_db <- dbConnect(RSQLite::SQLite(), 
    "../../MASTERS/MetaAnalysis/Data/metabeaver.db")
```

## Tables

responses, 
projects, 
questions, 
answers_text, 
answers_mc, 
answers_ls, 
answers_ca.

### responses 
 
    - This table will contain all responses submitted to the Google Forms 
    survey and will contact columns for response ID (resp_id) and project ID 
    (proj_id). Response IDs will be generated electronically based on the order 
    of survey submission and each project will be manually assigned a unique 
    character code to distinguish it among others.

```{r, eval = FALSE, echo = TRUE}
    dbExecute(metabeaver_db, "CREATE TABLE responses (
          resp_id varchar (5) NOT NULL PRIMARY KEY,
          FOREIGN KEY(proj_id) REFERENCES projects(proj_id)
          );")
```

### projects

    - This table will contain information about all respondents projects and 
    contact information and will contain columns for proj_id, proj_email, 
    proj_name,	proj_agency,	proj_501c3,	proj_called,	proj_lead,	
    proj_lead_alt, and	proj_location. The proj_id column will serve as the 
    foreign key linking this table to the Responses table.

```{r, eval = FALSE, echo = TRUE}
    dbExecute(metabeaver_db, "CREATE TABLE projects (
          proj_id varchar(5) PRIMARY KEY
          proj_email text,
          proj_name text,
          proj_agency varchar (15) CHECK (proj_agency IN ('State', 'Federal', 
              'Tribal', 'Non Profit', 'For Profit')),
          proj_501c3 varchar (15) CHECK (proj_501c3 IN ('501c3', 
              'fiscal sponsor')),
          proj_called text,
          proj_lead varchar (5) CHECK (proj_lead IN ('yes', 'no')),
          proj_lead_alt text,
          proj_location text
          );")
```

### questions

    -This table will contain all of the questions and type of questions that 
    will be asked in the Google Forms survey and will contain columns for 
    quest_id, quest_type, and questions.

```{r, eval = FALSE, echo = TRUE}
    dbExecute(metabeaver_db, "CREATE TABLE questions (
          quest_id varchar text PRIMARY KEY
          questions text,
          quest_type varchar (5) CHECK (quest_type IN ('text', 'mc', 'ls', 
              'ca')),
          );")
```

### answers_text

    -This table will contain all answers to short and long answer questions and
    will contain columns for text_id, answer, resp_id, and	quest_id. The 
    resp_id and quest_id columns will serve as foregin keys linking this table 
    to the Responses and Questions tables.

```{r, eval = FALSE, echo = TRUE}
    dbExecute(metabeaver_db, "CREATE TABLE answers_text (
          text_id text PRIMARY KEY,
          answer text,
          FOREIGN KEY(resp_id) REFERENCES responses(resp_id)
          FOREIGN KEY(quest_id) REFERENCES questions(quest_id)
          );")
```

### answers-mc

    -This table will contain all answers to multiple choice questions and will 
    contain columns for mc_id, answer, resp_id, and	quest_id. The resp_id and
    quest_id columns will serve as foregin keys linking this table to the 
    Responses and Questions tables.

```{r, eval = FALSE, echo = TRUE}
    dbExecute(metabeaver_db, "CREATE TABLE answers_mc (
          mc_id text PRIMARY KEY,
          answer text,
          FOREIGN KEY(resp_id) REFERENCES responses(resp_id)
          FOREIGN KEY(quest_id) REFERENCES questions(quest_id)
          );")
```

### answers_ls

    -This table will contain all answers to linear scale questions and will 
    contain columns for ls_id, answer, resp_id, and	quest_id. The resp_id and 
    quest_id columns will serve as foregin keys linking this table to the 
    Responses and Questions tables.

```{r, eval = FALSE, echo = TRUE}
    dbExecute(metabeaver_db, "CREATE TABLE answers_ls (
          ls_id text PRIMARY KEY,
          answer text,
          FOREIGN KEY(resp_id) REFERENCES responses(resp_id)
          FOREIGN KEY(quest_id) REFERENCES questions(quest_id)
          );")
```

### answers_ca

    -This table will contain all answers to check all that apply questions and 
    will contain columns for ca_id, answer_1,	answer_2,	answer_3,	answer_4,	
    answer_5, resp_id, and	quest_id. The resp_id and quest_id columns will 
    serve as foregin keys linking this table to the Responses and Questions 
    tables.

```{r, eval = FALSE, echo = TRUE}
    dbExecute(metabeaver_db, "CREATE TABLE answers_ca (
          ca_id text PRIMARY KEY,
          answer text,
          FOREIGN KEY(resp_id) REFERENCES responses(resp_id)
          FOREIGN KEY(quest_id) REFERENCES questions(quest_id)
          );")
```


## Relational Database Diagram

```{r, eval=FALSE, echo=FALSE}
library(knitr)
```

```{r my-fig, fig.cap= "Relational Database Diagram", fig.align='center', out.width='100%', eval=TRUE, echo=FALSE}
knitr::include_graphics("/Users/mollyalves/MASTERS/Bookdown/my_bookdown_website/ReproDat_Assignment3.pdf", rel_path= getOption("knitr.graphics.rel_path", TRUE))
```
