# Data Input Testing

For the purposes of this assignment I will load my raw data, responses, projects, questions, and answers_text tables as a test of what the data will look like in R. 

## Load Raw Data from Survey

```{r, eval=TRUE, echo=FALSE}
library(tidyverse)
```

```{r, eval=TRUE, echo=FALSE}
library(readxl)
```

```{r, eval=TRUE}
RawData_test <- readxl::read_excel ("~/MASTERS/Bookdown/GoogleFormRespTEST.xlsx")
RawData_test
```

## responses

```{r, eval=TRUE}
Responses_test <- readxl::read_excel ("~/MASTERS/Bookdown/Responses.xlsx")
Responses_test
```

## projects

```{r, eval=TRUE}
Projects_test <- readxl::read_excel ("~/MASTERS/Bookdown/Projects.xlsx")
Projects_test
```

## questions

```{r, eval=TRUE}
Questions_test <- readxl::read_excel ("~/MASTERS/Bookdown/Questions.xlsx")
Questions_test
```

## answers_text

```{r, eval=TRUE}
Answers_text_test <- readxl::read_excel ("~/MASTERS/Bookdown/Answers_text.xlsx")
Answers_text_test
```

## combining tables

Combining Answers_text_test to Questions using key quest_id and Responses using key resp_id.

```{r, eval=TRUE}
Comb_test <- Answers_text_test %>%
  left_join(Questions_test, by = "quest_id") %>%
  left_join(Responses_test, by = "resp_id")
```

```{r, eval=TRUE}
Comb_test
```

Combining new Comb_test to Comb_test2 to include Projects using key proj_id.

```{r, eval=TRUE}
Comb_test2 <- Comb_test %>%
  left_join(Projects_test, by = "proj_id")

```

```{r, eval=TRUE}
Comb_test2
```

* I realize I am having issues with duplicates by text_id field. Will need to 
consult and rectify to figure out how to make the data not duplicate, especially
when other answers_ tables are added.